Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2017-12-06 Ben_Manuscripts/structure_paper/Draft.tex
Turning outline into draft - intro text nearly done

\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\title{Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes}
\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Joe Yelk \and Matthew Glaser \and Xunda Feng \and Michael R. Shirts} 
\begin{document}
  \bibliographystyle{ieeetr}
  \graphicspath{{./figures/}}
  \maketitle
  \section*{Introduction}

  Nanostructured membrane materials have become increasingly popular for 
  aqueous separations applications such as desalination and biorefinement
  because they offer the ability to control membrane architecture at the
  atomic scale allowing the design of solute-specific separation membranes. \cite{humplik_nanostructured_2011}
  \begin{itemize}
    \item Most membrane-based aqueous separations of small molecules can 
    be achieved using reverse osmosis (RO) or nanofiltration (NF) \cite{van_der_bruggen_review_2003}
  \end{itemize}

  While RO and NF have seen many advances in the past few decades, they 
  are far from perfect separation technologies.
  \begin{itemize}
    \item \textit{RO membranes}
    \item Inconsistent performance : Current state-of-the-art RO membranes are unstructured with
    tortuous and polydisperse diffusion pathways which leads to 
    inconsistent performance \cite{song_nano_2011}
    \item High energy requirements : Necessarily high feed pressures 
    drive up energy requirements which strains developing regions and
    contributes strongly to CO\textsubscript{2} emissions. \cite{mcginnis_global_2008}
    \item Separation based on differences in solubility and diffusivity:
%MRS2: couldn't you argue that the fact that they diffuse and dissolve at different rates means that it makes it possible to design targeted separations?
%BJC: right, I say something like that in the sentence following this one. It would be more challenging to design a targeted separation 
% especially if the feed is complex
    Moreover, designing RO membranes to achieve targeted separations of 
    specific solutes in a complex feed solution is nearly impossible because various solutes dissolve
    into and diffuse through the polymer matrix at different rates. \cite{wijmans_solution-diffusion_1995}
    \item With optimization, one can exploit these differences to create a functional
    selective barrier.
    \item \textit{NF membranes}
    \item NF was introduced as an intermediate between RO and ultrafiltration,
    having the ability to separate organic matter and salts on the order of 
    one nanometer in size.
%MRS2: is ``well-defined'' the right word if there is a ``pore size distribution''?
%BJC: By well-defined, I'm thinking of cylinders versus polymer matrix. One is definitely more
% defined than the other. What is the right word for that? unambiguous? explicit?
%MRS3: hmm.  Maybe look and see what other people call them when describing NF membranes.
    \item Larger and well-defined pores drive down energy requirements while
    still affording separation of solutes as small as ions to some degree \cite{van_der_bruggen_review_2003}
    \item NF is often used as a precursor to reverse osmosis
    \item Unfortunately, NF membranes, like RO, possess a pore size 
    distribution which limits their ability to perform precise separations \cite{bowen_modelling_2002}
  \end{itemize}

  Nanostructured membranes can bypass many of the performance issues which
  plague traditional NF and RO membranes.
  \begin{itemize}
    \item Tune size and functionality of building blocks to control pore
    size and shape: One can accomplish targeted separations with high 
    selectivity by tuning shape, size and functionality of the molecular
    building blocks which form these materials. 
    \item As a result, solute rejecting pores can have their sizes tuned
    uniformly, resulting in strict size cut-offs.
    \item Entirely different mechanisms may govern transport in a given
    nanostructured material which can inspire novel separation techniques.
  \end{itemize}

  Development of nanostructured materials has been limited by the ability
  to synthesize and scale various fundamentally sound technologies.
  \begin{itemize}
    \item Graphene sheets are atomically thick which results in excellent
    permeability but defects during manufacturing severely impact 
    selectivity. \cite{cohen-tanugi_multilayer_2016}
    \item Molecular dynamics simulations of carbon nanotubes show
    promise \cite{humplik_nanostructured_2011} but synthetic techniques are 
    unable to achieve scalable alignment and pore monodispersity.\cite{hata_water-assisted_2004,maruyama_growth_2005}
    \item Zeolites have sub-nm pores with a narrow pore size 
    distribution and MD simulations exhibit complete rejection of solvated ions, \cite{murad_molecular_1998}
    however, experimental rejection was low and attributed to interstitial
    defects formed during membrane synthesis \cite{li_desalination_2004}
    \item There is a need for a scalable nanostructured membrane
  \end{itemize}

  Self assembling lyotropic liquid crystals (LLCs) are a suitable candidate for
  aqueous separation applications. 
  \begin{itemize}
    \item LLCs share the characteristic ability of nanostructured membrane
    materials to create highly ordered structures with the added benefits
    of low cost and synthetic techniques feasible for 
    large scale production \cite{feng_scalable_2014}
    \item Neat liquid crystal monomer forms the thermotropic, Col\textsubscript{h}
    phase. The presence of water results in the H\textsubscript{II} phase.
    \item In both cases, monomers assemble into mesophases made of hexagonally
    packed, uniform size, cylinders with hydrophilic groups oriented inward
    towards the pore center and hydrophobic groups facing outward.
    \item H\textsubscript{II} and Col\textsubscript{h} phase systems created by
    the monomer named Na-GA3C11 have been extensively studied experimentally \cite{smith_ordered_1997, %BJC: IUPAC chemical name here?
    zhou_supported_2005,resel_h2-phase_2000,feng_scalable_2014,feng_thin_2016}. 
  \end{itemize}

  Research into LLC membranes has been revived in recent years.
  \begin{itemize}
    \item During early stages of exploration, mesophases formed by Na-GA3C11 could not be macroscopically
    aligned, resulting in low flux membranes, and no clear route towards 
    scalable and economical filtration. 
    \item In 2014, Feng et al. showed that the mesophases could be aligned 
    using a magnetic field with subsequent crosslinking to lock the structure
    in place \cite{feng_scalable_2014}
    \item In 2016, Feng et al. showed that the same result could be obtained 
    using a technique termed soft confinement \cite{feng_thin_2016}.
  \end{itemize}

  % BJC: Not sure this figure needs to be in the paper. 
  %MRS2: good question.  It helps give people context, which is necessary to move forward.  Perhaps 
  %leave it in for now, though may need to get permission to reprint it.
  \begin{figure}
	\centering
	\includegraphics[width=\linewidth]{soft_confinement.png}
	\caption{The wedge shaped liquid crystal monomer (a) self assembles into 
	mesophases with hexagonally packed pores (b). The pores are made of 
	stacked monomer disks. A sub-micron-thick film is created by casting a 
	dilute solution of Na-GA3C11/THF solution onto a silicon substrate and 
	and allowing the solvent to evaporate. The thin film contains nanoporous 
	columns which lie parallel to the film plane. (d) When a soft PDMS pad is 
	imposed to the thin film, with subsequent thermal annealing, the columns
	align perpendicular to the film plane. (e) Photo-cross-linking of the
	aligned film creates a mechanically stable thin film with vertically 
	aligned nanopores}~\label{fig:soft}
  \end{figure}

  A molecular level understanding of LLC membrane structure, enabled by molecular
  dynamics simulations, will provide guidelines to reduce the large chemical space
  available to design monomers for creation of separation-specific membranes.
  \begin{itemize}
    \item Over the past 20 years, H\textsubscript{II} phase LLC membrane studies have been limited primarily
    to Na-GA3C11 with some characterization done after minor structural modifications
    \item Resel et al. varied the length of the monomer tails and the counterion used and 
    observed its affect on pore spacing \cite{resel_structural_2000}.
    \item Rejection studies show that this membrane can not perform separations of
    solutes less than 1.2 nm in diameter because the pores are too large \cite{zhou_supported_2005}.
    \item  We do not yet understand how to controllably reduce the effective pore size or 
    how to tune the chemical environment in the nanopores for effective water
    desalination or small organic molecule separations.
    \item It will be challenging to efficiently narrow down the large design space in 
    a laboratory setting without a robust model.
    \item The only source of predictive modeling for LLC systems have been macroscopic models 
    which likely do not adequately describe transport at these length scales. % BJC: Reference. I think it is just w.r.t. bicontinuous cubic
%MRS2: not quite sure of the phrasing here on next two points. Something more a long the lines of the choice of head group 
%may allow tuning rejection of solutes based on size?
%BJC: okay tried again
    \item The choice of head group may allow us to tune pore size for size exclusion driven separations
%MRS3: choice of counterion also affects size.  Counterion type probably doesn't affect Donnan potential that much IRCC, more the total amount of counterion.
    \item Choice of counterion may influence the establishment of a Donnan potential
    affecting the degree to which the membrane can exclude charged species.
    \item A good molecular model should incorporate a detailed picture of the nanoscopic pore 
    structure which will be crucial to understanding the role of monomer structure in 
    membrane design.
    \item Molecular dynamics simulations will provide the required level of detail
  \end{itemize}

  %BJC: Figure here showing previous level of detail compared to atomistic level of detail
  %MRS2: provenance of the atomistic figure could be explained better in the caption. It also looks disordered. Will eventually need a higher resolution figure for the previous understanding pore.
  %BJC: Okay. The picture here is of the "ordered pore" phase. It looks disorderd from this angle. I could use a different slice of the membrane to see if it looks any better
%MRS: if this is ordered, OK.  Maybe could try to rotate it a bit more towards the reader.
  \begin{figure}
  \centering
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{nanopore_undetailed.jpg}
		\caption{}~\label{fig:undetailed_pore}
	\end{subfigure}
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{detailed_pore.png}
		\caption{}~\label{fig:detailed_pore}
	\end{subfigure}
  \caption{(a) Our previous understanding of the pore structure allows us to speculate
	   about separation behavior. (b) A detailed molecular model will allow us to
	   directly observe solute transport. Here, four stacked layers of 5 monomers
           are pictured atomistically. The hydrophilic region is in red and the 
	   hydrophoic region is colored blue.}~\label{fig:detail}
  \end{figure}

  Our approach to constructing a general model will follow the development of a
  model of a specific LLC membrane with sufficient experimental characterization.
    \begin{itemize}
	    \item We have chosen to focus on assemblies formed by Na-GA3C11
	    \item We have also narrowed our scope to the development of 
	    a model of the Col\textsubscript{h} phase membrane.
	    \item Compared to the H\textsubscript{II} phase, the Col\textsubscript{h}
	    phase is a simpler starting point, due to the absence of water, and has
	    detailed experimental WAXS patterns useful for reconstructing structural data.  
    \end{itemize}

  Despite having structural data, there is still information which
  experiment cannot definitively answer. There are several key
  questions that we intend to answer 
%MRS3: we can't ``answer'' for sure, since it's a model, and may omit things. Could put ``several key questions we will investigate'' or ``hope to provide evidence for or against'', or something like that.
which will be laid out and numbered
  in subsequent paragraphs.

%BJC: the following just seems like filler now that I've reorganized
%   A clear picture of the nanoscopic LLC membrane structure, gained by building 
%   a molecular model will provide evidence to answer existing and newly proposed
%   questions.
%     \begin{itemize}
%     \item Despite having structural data, there is still information which 
%     experiment cannot definitively answer
%     \end{itemize}

%MRS: break this down into more hierarchy - there are 11 separate points.  Can they be grouped at all for clearer understanding? elucidate what the aspects are we need a clearer picture. 
%BJC: I moved the logic for choice of monomer to system to model to a separate paragraph (above this). I then moved the other three things I talk about into their own paragraphs to keep the ideas separate (following paragraphs).
%MRS: since the questions we answer in the paper have a lot to do with the structure of the membranes, somewhere relatively early in the paper we need to lay out the facts that 1) these membranes could be really good (I think you do establish this) 2) we really would need to know the structure better to really do useful things with these, and 3) MD is a very helpful way to gain more information about the structure, because of the limited range of experiments we can do with these systems. That is the main rationale, and it should be made clear fairly early in the introduction.  Very important to make your story absolutely as clear as possible.
%BJC: I moved and edited a paragraph that was originally later on to be 2 above this one. I think it does a better job addressing points 2 and 3. And now it addresses those points earlier in the intro (as early as it could go where I think it still makes sense in context)

%BJC: How question (1) and (2) used to be ordered:
%
%  (1) Do monomers partition into and persist as defined monomer layers?
%  H\textsubscript{II} and Col\textsubscript{h} phase LC membrane pores are 
%  thought to be composed of monomer layers stacked on top of each other. 
%  \begin{itemize}
%  	\item Their existence is supported by experimental evidence of strong 
%	$\pi$-$\pi$ stacking interactions in the direction perpendicular to the
%	membrane plane.
%	\item $\pi$-$\pi$ stacking will only occur between monomer head groups which
%	leaves no description of what is happening in monomer tail region
%	\item It is possible that $\pi$-$\pi$ stacking occurs vertically 
%	with no order in reference to neighboring stacked columns of the same pore.  % BJC: not sure if this is actually true
%  \end{itemize}
%
%  (2) If layers do exist, how many monomers constitute a single layer?
%  There has been no definitive answer to the question in literature.
%  \begin{itemize}
%    \item A simple molecular simulation study of a similar molecule suggested
%    that there are 4 monomers in each layer. Their estimation is based on a
%    simulated system containing only 16 total monomers which likely does not sufficiently
%    model the chemical environment present in the real system.~\cite{zhu_methacrylated_2006}. 
%    \item A separate calculation based on the volume of the liquid crystal monomers proposes
%    that there are seven monomers in each layer~\cite{resel_structural_2000}. 
%    \item A molecular model orders of magnitude larger than any other reported atomistic 
%    liquid crystal membrane simulations has the best chance of directly answering this question.
%  \end{itemize}

  Monomers in the Col\textsubscript{h} system are theorized to be partitioned
  into stacked layers which form columnar pores. There has been no definitive
  answer in literature regarding the number of monomers in each layer. 
%MRS3: the intro to the list talks about only ``numbers of monomers in each layer'', whereas the list below talks about several questions relating to layers. Can you rephrase so it's more general? Maybe just take out that sentence above.
We want to
  know 
\begin{enumerate}
\item If layers do exist, how many monomers constitute a single layer? \label{point:monomernum}
  \begin{itemize}
    \item A simple molecular simulation study of a similar molecule suggested
    that there are 4 monomers in each layer. Their estimation is based on a
    simulated system containing only 16 total monomers which likely does not sufficiently
    model the chemical environment present in the real system.~\cite{zhu_methacrylated_2006}. 
    \item A separate calculation based on the volume of the liquid crystal monomers proposes
    that there are seven monomers in each layer~\cite{resel_structural_2000}. 
    \item A molecular model orders of magnitude larger than any other reported atomistic 
    liquid crystal membrane simulations has the best chance of directly answering this question.
    \item We can directly change the layer composition and note its effect on membrane structure.
  \end{itemize}

 \item Does our model support the existence of layers and if so, how well defined
  are the layers? \label{point:layers}
  \begin{itemize}
       \item Experimentally, their existence is supported by evidence of strong 
       $\pi$-$\pi$ stacking interactions in the direction perpendicular to the
       membrane plane.
       \item $\pi$-$\pi$ stacking will only occur between the aromatic monomer head groups which
       leaves no description of what is happening in the monomer tail region
       \item The tails may entangle isotropically while stacking order is maintained
       among headgroups. 
  \end{itemize}

   \item How do monomers in each layer position themselves with respect to surrounding 
   layers? \label{point:orientation}
%     Even if we knew the number of monomers in each layer, we still would not know how 
%     monomers in each layer are positioned with respect to other layers. 
   \begin{itemize}
      \item The $\pi$-$\pi$ stacking interactions may be a driving force of self assembly 
      in this system\cite{gazit_possible_2002} %is thought to be $\pi$-$\pi$ stacking interactions between aromatic headgroups \cite{gazit_possible_2002}. 
      \item Gas phase ab initio studies of benzene dimers have shown a clear energetic
      advantage for parallel displaced and T-shaped $\pi$-$\pi$ stacking conformations versus a
      sandwiched conformation ~\cite{sinnokrot_estimates_2002}.
      \item Substituted benzene rings exhibit an even stronger $\pi$-$\pi$ stacking 
      attraction which favors the parallel displaced configuration in all cases
      except where the substitutions are extremely electron withdrawing
      \cite{waller_hybrid_2006,ringer_effect_2006}.
      \item We can use simulated X-ray diffration patterns to compare the two 
      stacking configurations. 
   \end{itemize}

  \item Can the system exist in other metastable states or phases that are not
  accessed during experiments? \label{point:metastable}
  There remains the possibility that there is more than one metastable state 
  associated with a given LLC system.
  \begin{itemize}
    \item Simulating a membrane atomistically will require many atoms which further
    limits the timescales acessible with MD
    \item It is reasonable to expect that we will generate configurations which 
    are kinetically trapped in a metastable free energy basin
    \item We must be able to identify which state is produced experimentally and 
    why others are not.
  \end{itemize}

  \item What constitutes a pore and how well-defined are the pore regions? \label{point:poredefinition}
  \begin{itemize}
	\item The limited picture that experiment provides tells us that there are
        hexagonally packed, hydrophilic regions where transport is likely to occur
	\item One may instinctively assume that these regions are tube-like pathways
	\item We will explore the composition of the pores and the partition
	between the hydrophilic and hydrophobic regions. 
  \end{itemize}

  \item Is it necessary to include any water in order to appropriately model the 
  Col\textsubscript{h} phase? \label{point:water}
  \begin{itemize}
	\item While the Col\textsubscript{h} phase is described as dry, it is 
          %MRS3: ``possible'' -> likely, and give some explanations why we think likely?
	possible that small amounts of ambient water may be leached into the system.
	\item The hydrogen bonding network formed by the water may play a role 
        in structuring the pore.
	\item We can use simulated X-ray diffraction patterns to see if there is
        any meaningful structural difference between a "dry" and "wet" system
  \end{itemize}
  \end{enumerate}

@@

  We chose the layer spacing for the initial configuration based on R-$\pi$ 
  and then allowed system to readjust during equilibration.
  \begin{itemize}  
    \item Each monomer was rotated so the plane of the aromatic head groups would
    be coplanar with the xy plane.
    \item We explore two different initial layer spacings
    \item The first is exactly equal to R-$\pi$ with layers placed so aromatic
    rings are stacked 3.7 \angstrom~ apart in the z-direction.
    \item A second system is explored with an initial layer spacing of 5 \angstrom
%MRS3: at least state in the main body what went wrong with it in a sentence or so, with details in supplemental. 
   \item A third system with an initial layer spacing of 10 \angstrom was briefly
    explored and the reader can learn more about it in the Supplemental Information.
% BJC: Move all this lower down to be with the rest of the equilibrium calculations
%    \item To quantify the degree of layering in our system, we calculated
%    a spatial correlation function, $g(z)$, measured along the z-axis 
%    (perpendicular to the membrane plane)
%    \item To calculate $g(z)$, we binned the z component distances between 
%    the center of mass of each benzene ring and all others of the same pore 
%    over 50 ns of equilibrated trajectory and then normalized by the average
%    number density.
%    \item We compare the degree of layering between systems based on the
%    amplitude of the first peak in $g(z)$. We halve the difference between the
%    maximum of the first peak and the following minimum. We compare the difference
%    to the mean to get a percentage deviation from the average number density.
%    \item To extract the average distance between layers we applied a discrete 
%    fourier transform to $g(z)$ and extracted the highest intensity frequency 
  \end{itemize}

>>>>

\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{setspace}
\doublespacing

\title{Understanding the nanoscale structure of hexagonal phase
lyotropic liquid crystal membranes}
\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble
\and Joe Yelk \and Matthew Glaser \and Xunda Feng \and Michael R.
Shirts}

\begin{document}

  \bibliographystyle{ieeetr}
  \graphicspath{{./figures/}}
  \maketitle

  \section*{Introduction}

  Nanostructured membrane materials have become increasingly popular for
  aqueous separations applications such as desalination and biorefinement because
  they offer the ability to control membrane architecture at the atomic scale
  permitting the design of solute-specific separation membranes.
  \cite{humplik_nanostructured_2011} Most membrane-based aqueous separations of
  small molecules can be achieved using reverse osmosis (RO) or nanofiltration
  (NF). \cite{van_der_bruggen_review_2003}

  While RO and NF have seen many advances in the past few decades, they are far
  from perfect separation technologies. Current commericial RO membranes are thin
  film composite membranes with a porous support layer and an active layer made
  of a dense polyamide polymer matrix.  The membranes are unstructured with
  tortuous and polydisperse diffusion pathways. Separation occurs as solutes
  dissolve into and diffuse through voids in the polymer matrix at different
  rates.\cite{wijmans_solution-diffusion_1995} With optimization, one can exploit
  these differences to create a functional selective barrier. High feed pressures
  are required in order to achieve economical solvent flux. The largest
  application of reverse osmosis is desalination. A typical seawater desalination
  process requires feed pressures in the range of 800 to 1000 psi in order to
  overcome osmotic pressure. \cite{fritzmann_state---art_2007} Only 0.5 \% of the
  world's water is fresh. Desalination is an important source of potable water,
  necessary in order to keep up with demand generated by a rapidly growing global
  population. Although RO is currently the cheapest form of desalination, the
  cost must be further decreased in order to meet demand. By designing better
  membranes for desalination, we can achieve higher water fluxes and lower feed
  pressure requirements which will decrease the cost of fresh water production.
  \cite{humplik_nanostructured_2011}.

  % financially straining developing regions and contributing strongly to
  % CO\textsubscript{2} emissions. \cite{mcginnis_global_2008} Moreover,
  % designing RO membranes to achieve targeted separations of specific solutes
  % in a complex feed solution is nearly impossible

  NF was introduced as an intermediate between RO and ultrafiltration, having
  the ability to separate organic matter and salts on the order of one nanometer
  in size. Explicit pore pathways running through the thickness of the membrane
  permit high solvent fluxes at lower pressures than RO. NF membranes typically
  have a surface charge resulting from ionizable groups which affords separation
  of ions smaller than the pore readius by Donnan exclusion.
  \cite{van_der_bruggen_review_2003} NF is often used as a precursor to reverse
  osmosis since it can efficiently remove a significant portion of dissolved
  solutes. Following NF pretreatment, RO can further purify the permeate at lower
  pressure. Unfortunately, NF membranes, like RO, possess a pore size
  distribution which limits their ability to perform precise separations
  \cite{bowen_modelling_2002}. An NF membrane with high selectivity could offer
  the versatility to separate ions as well as small charged and uncharged
  molecules to the same degree as RO and at a significantly lower cost.

  Nanostructured membranes can bypass many of the performance issues which
  plague traditional NF and RO membranes. One can accomplish targeted separations
  with high selectivity by tuning shape, size and functionality of the molecular
  building blocks which form these materials. As a result, solute rejecting pores
  can have their sizes tuned uniformly, resulting in strict size cut-offs.
  Entirely different mechanisms may govern transport in a given nanostructured
  material which can inspire novel separation techniques.

  Development of nanostructured materials has been limited by the ability to
  synthesize and scale various fundamentally sound technologies.  Graphene sheets
  are atomically thick which results in excellent water permeability but defects
  during manufacturing severely impact selectivity.
  \cite{cohen-tanugi_multilayer_2016} Molecular dynamics simulations of carbon
  nanotubes show promise \cite{humplik_nanostructured_2011} but synthetic
  techniques are unable to achieve scalable alignment and pore monodispersity.
  \cite{hata_water-assisted_2004,maruyama_growth_2005} Zeolites have sub-nm pores
  with a narrow pore size distribution and MD simulations exhibit complete
  rejection of solvated ions, \cite{murad_molecular_1998} however, experimental
  rejection was low and attributed to interstitial defects formed during membrane
  synthesis. \cite{li_desalination_2004} There is a need for a scalable
  nanostructured membrane.

  Self assembling lyotropic liquid crystals (LLCs) are a suitable candidate for
  aqueous separation applications. LLCs share the characteristic ability of
  nanostructured membrane materials to create highly ordered structures with the
  added benefits of low cost and synthetic techniques feasible for large scale
  production.  \cite{feng_scalable_2014} LLC systems created by the monomer named
  Na-GA3C11 have been extensively studied experimentally.
  \cite{smith_ordered_1997,zhou_supported_2005,resel_h2-phase_2000,feng_scalable_2014,feng_thin_2016}
  Neat liquid crystal monomer forms the thermotropic, Col\textsubscript{h} phase.
  The presence of ca. 10 wt \% water results in the H\textsubscript{II} phase. In
  both cases, monomers assemble into mesophases made of hexagonally packed,
  uniform size, cylinders with hydrophilic head groups oriented inward towards
  the cylinder center.  The hydrophilic region can act as a pore for aqueous
  separations.  One can envision tailoring the pore region for specific
  separations by changing the monomer chemsitry.

  Research into LLC membranes has been revived in recent years.  During early
  stages of exploration, mesophases formed by Na-GA3C11 could not be
  macroscopically aligned, resulting in low flux membranes, and no clear route
  towards scalable and economical filtration. In 2014, Feng et al. showed that
  the mesophases could be aligned using a magnetic field with subsequent
  crosslinking to lock the structure in place. \cite{feng_scalable_2014} In 2016,
  Feng et al. showed that the same result could be obtained using a technique
  termed soft confinement. \cite{feng_thin_2016}

  % BJC: Not sure this figure needs to be in the paper. 
  %MRS2: good question.  It helps give people context, which is necessary to
  %move forward.  Perhaps leave it in for now, though may need to get
  %permission to reprint it.
  \begin{figure} \centering
  \includegraphics[width=\linewidth]{soft_confinement.png} \caption{The wedge
	  shaped liquid crystal monomer (a) self assembles into mesophases with
		  hexagonally packed pores (b). The pores are made of stacked monomer disks. A
		  sub-micron-thick film is created by casting a dilute solution of Na-GA3C11/THF
		  solution onto a silicon substrate and and allowing the solvent to evaporate.
		  The thin film contains nanoporous columns which lie parallel to the film plane.
		  (d) When a soft PDMS pad is imposed to the thin film, with subsequent thermal
		  annealing, the columns align perpendicular to the film plane. (e)
		  Photo-cross-linking of the aligned film creates a mechanically stable thin film
		  with vertically aligned nanopores}~\label{fig:soft} \end{figure}

  Our current understanding of LLC systems is not rich enough to be able to
  precisely design membranes for specific separations. Over the past 20 years,
  H\textsubscript{II} phase LLC membrane studies have been limited primarily to
  Na-GA3C11 with some characterization done after minor structural modifications.
  Resel et al. varied the length of the monomer tails and the counterion used and
  observed its affect on pore spacing \cite{resel_structural_2000}.  Their study
  offers no insight into dynamics within the pore. Rejection studies show that
  membranes formed by NA-GA3C11 can not perform separations of solutes less than
  1.2 nm in diameter because the pores are too large \cite{zhou_supported_2005}.
  We do not yet understand how to controllably reduce the effective pore size or
  how to tune the chemical environment in the nanopores for effective water
  desalination or small organic molecule separations. The only source of
  predictive modeling for LLC systems have been macroscopic models which likely
  do not adequately describe transport at these length scales.
  \cite{hatakeyama_water_2011} It will be challenging to efficiently narrow down
  the large design space in a laboratory setting without a robust model.

  A molecular level understanding of LLC membrane structure, enabled by
  molecular dynamics simulations, will provide guidelines to reduce the large
  chemical space available to design monomers for creation of separation-specific
  membranes. A good molecular model should incorporate a detailed picture of the
  nanoscopic pore structure which will be crucial to understanding the role of
  monomer structure in solute transport and membrane design. Models resulting
  from molecular dynamics simulations will provide the required level of detail.
  We can directly observe solute transport and suggest governing mechanisms. We
  can observe how the choice of head group may influence pore size for size
  exclusion driven separations. We can interchange counterions which may
  influence both the pore size and the strength of the Donnan potential which
  affects the degree to which the membrane can exclude charged species.

  % BJC: improve this figure
  \begin{figure}
  \centering
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{nanopore_undetailed.jpg}
		\caption{}~\label{fig:undetailed_pore}
	\end{subfigure}
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{detailed_pore.png}
		\caption{}~\label{fig:detailed_pore}
	\end{subfigure}
  \caption{(a) Our previous understanding of the pore structure allows us to speculate
	   about separation behavior. (b) A detailed molecular model will allow us to
	   directly observe solute transport. Here, four stacked layers of 5 monomers
           are pictured atomistically. The hydrophilic region is in red and the 
	   hydrophoic region is colored blue.}~\label{fig:detail}
  \end{figure}

  %BJC: I think the first sentence of the following paragraph is
  %necessary to put somewhere, but maybe not in this spot exactly
  In order to appropriately model transport, we must gain a thorough
  understanding of the nanoscopic structure of LLC membranes.  Our approach to
  constructing a general model will follow the development of a model of the
  assembly formed by Na-GA3C11 since it has sufficient experimental
  characterization. We have also narrowed our scope to the development of a model
  of the Col\textsubscript{h} phase membrane. Compared to the H\textsubscript{II}
  phase, the Col\textsubscript{h} phase is a simpler starting point, due to the
  absence of water, and has detailed experimental Wide-angle X-ray scattering
  (WAXS) patterns useful for reconstructing structural data.

  Despite having structural data, there is still information which experiment
  cannot definitively answer. There are several key questions that we will
  investigate which will be laid out and numbered in subsequent paragraphs.

  %BJC: commenting out :There has been no definitive answer in literature
  %regarding the number of monomers in each layer.  MRS3: the intro to the list
  %talks about only ``numbers of monomers in each layer'', whereas the list
  %below talks about several questions relating to layers. Can you rephrase so
  %it's more general? Maybe just take out that sentence above.

  Monomers in the Col\textsubscript{h} system are theorized to be partitioned
  into stacked layers which form columnar pores. We want to know

  \begin{enumerate}

  \item If layers do exist, how many monomers constitute a single layer? \label{point:monomernum}

  A simple molecular simulation study of a similar molecule suggested that
  there are 4 monomers in each layer. Their estimation is based on a simulated
  system containing only 16 total monomers which likely does not sufficiently
  model the chemical environment present in the real system.
  \cite{zhu_methacrylated_2006}.  A separate calculation based on the volume of
  the liquid crystal monomers proposes that there are seven monomers in each
  layer \cite{resel_structural_2000}.  A molecular model orders of magnitude
  larger than any other reported atomistic liquid crystal membrane simulations
  has the best chance of directly answering this question.  We will directly
  change the layer composition and note its effect on membrane structure.

 \item Does our model support the existence of layers and if so, how well
 defined are the layers? \label{point:layers}

  Experimentally, their existence is supported by evidence of strong $\pi$-$\pi$
  stacking interactions in the direction perpendicular to the membrane plane.
  $\pi$-$\pi$ stacking will only occur between the aromatic monomer head groups
  which leaves no description of what is happening in the monomer tail region.
  The tails may entangle isotropically while stacking order is maintained among
  headgroups.

  \item How do monomers in each layer position themselves with respect to
  surrounding layers? \label{point:orientation}

  The $\pi$-$\pi$ stacking interactions may be a driving force of self assembly
  in this system. \cite{gazit_possible_2002} Gas phase ab initio studies of
  benzene dimers have shown a clear energetic advantage for parallel displaced
  and T-shaped $\pi$-$\pi$ stacking conformations versus a sandwiched
  conformation ~\cite{sinnokrot_estimates_2002}. Substituted benzene rings
  exhibit an even stronger $\pi$-$\pi$ stacking attraction which favors the
  parallel displaced configuration in all cases except where the substitutions
  are extremely electron withdrawing.
  \cite{waller_hybrid_2006,ringer_effect_2006}. We can use simulated X-ray
  diffration patterns to compare the two stacking configurations.

  \item Can the system exist in other metastable states or phases that are not
  accessed during experiments? \label{point:metastable}

  There remains the possibility that there is more than one metastable state
  associated with a given LLC system. Simulating a membrane atomistically will
  require many atoms which limits the timescales acessible with MD. It is
  reasonable to expect that we will generate configurations which are kinetically
  trapped in a metastable free energy basin. We must be able to identify which
  state is produced experimentally and why others are not.

  \item What constitutes a pore and how well-defined are the pore regions? \label{point:poredefinition}

  The limited picture that experiment provides tells us that there are
  hexagonally packed, hydrophilic regions where transport is likely to occur.
  One may instinctively assume that these regions are tube-like pathways. We will
  explore the composition of the pores and the partition between the
  hydrophilic and hydrophobic regions.

  \item Is it necessary to include any water in order to appropriately model
  the Col\textsubscript{h} phase? \label{point:water}

  While the Col\textsubscript{h} phase is described as dry, it is 
  %MRS3: ``possible'' -> likely, and give some explanations why we think
  %likely? 
  likely that small amounts of ambient water may be leached into the system. The
  hydrogen bonding network formed by the water may play a role in structuring the
  pore.  We can use simulated X-ray diffraction patterns to see if there is any
  meaningful structural difference between a "dry" and "wet" system

  \end{enumerate}

@@

  We chose the layer spacing for the initial configuration based on R-$\pi$ 
  and then allowed system to readjust during equilibration.
  \begin{itemize}  
    \item Each monomer was rotated so the plane of the aromatic head groups would
    be coplanar with the xy plane.
    \item We explore two different initial layer spacings
    \item The first is exactly equal to R-$\pi$ with layers placed so aromatic
    rings are stacked 3.7 \angstrom~ apart in the z-direction.
    \item A second system is explored with an initial layer spacing of 5 \angstrom
%MRS3: at least state in the main body what went wrong with it in a sentence or so, with details in supplemental. 
   \item A third system with an initial layer spacing of 10 \angstrom was briefly
    explored
   \item When layers are spaced out sufficiently, they tend to collapse on each other 
   while simultaneously slipping in between layers of other pores which lead to an
   artificially thick membrane with pores spaced closely together.
   \item The intereseted reader can learn more about it in the Supplemental Information.
% BJC: Move all this lower down to be with the rest of the equilibrium calculations
%    \item To quantify the degree of layering in our system, we calculated
%    a spatial correlation function, $g(z)$, measured along the z-axis 
%    (perpendicular to the membrane plane)
%    \item To calculate $g(z)$, we binned the z component distances between 
%    the center of mass of each benzene ring and all others of the same pore 
%    over 50 ns of equilibrated trajectory and then normalized by the average
%    number density.
%    \item We compare the degree of layering between systems based on the
%    amplitude of the first peak in $g(z)$. We halve the difference between the
%    maximum of the first peak and the following minimum. We compare the difference
%    to the mean to get a percentage deviation from the average number density.
%    \item To extract the average distance between layers we applied a discrete 
%    fourier transform to $g(z)$ and extracted the highest intensity frequency 
  \end{itemize}
